\documentclass[Final Report]{article}
\begin{document}



\title{Final Report}
\author{Raqeem Hussain}
\maketitle
\newpage



\section{}
During the early stages of the project, as a group we were not very proactive when developing the project as many of us were finding it difficult working together and completing the tasks we were assigned. Thus, we implemented weekly coding sessions. During our coding sessions, we would collaborate on the development of certain aspects of the site. With the integration of Live Share within these sessions, it gave the team the ability to further collaborate within sessions as we were able to work in parallel with each other; being able to code certain aspects of the site together and help any members of the team with tasks they had been assigned. This increased the productivity of the group overall and connected the group in a collaborative and innovative way. In future, we hope as a team that we would integrate these coding sessions earlier in the development of a project to increase productivity and collaboration in the group from day one. I hope, in future, to support the team more by aiding other team members with their coding and be more involved with organising coding sessions so that we can keep productivity high throughout the development of the project.

\section{}
To ensure that the delegation of tasks was done effectively during the project, we made sure that we were all aware of the extent of each member’s coding experience and their strengths. By doing this, we knew what tasks were appropriate for each team member, ensuring that their strengths were being utilized. Furthermore, when delegating the tasks we used GitHub projects, allowing team members to keep track of the tasks they were assigned and notify the rest of the team on the progress of their tasks by updating the status of the task with options of: “Todo”, “In Progress” or “Done”. Using GitHub, the team could keep track of where each team member was at with their tasks and be aware of whether features had been implemented or not. For future projects, the team should continue using these effective methods to delegate tasks but further endeavour on implementing more innovative ways of delegation. Subsequently, in future, I hope to give more in-depth updates on delegated tasks, supporting the team in knowing fully where I am at in a particular task. Moreover, I hope to aid with the delegation of tasks, assigning group members with tasks they are comfortable with.

\section {}
For my coursework for Introduction to Programming 1, I started coding for the coursework at a very late time. This meant that when it came to debugging the code for the coursework, I had a mountain of errors I had to resolve. Due to the number of errors which I encountered, I did not have enough time to fix all of them and finish the code for the program. Thus, the program which I handed in was finished in code but still had a multitude of errors, leading to me getting a substantially low mark in the coursework. Reflecting on this, when completing future coursework for modules, I need to make sure I start working on coursework as early as possible as this will provide me with sufficient time to complete the programming and test the code in order to resolve errors earlier. Likewise, I should test and debug code in coursework whilst working on it as this would allow me to find and resolve errors in a much more manageable way. Additionally, to support myself, in future, I should go to more lab sessions and ask questions on discussion boards to get help with coding and resolving errors when debugging.


\end{document}